\documentclass{article}
\input{preamble}

\title{latex-baseline}
\author{Istvan David}
\date{July 2025}

\begin{document}

\preprintlabel{xx.xxxx/xxxx}{\textbf{Here's an example of pre-print labeling. Use the \textbackslash\texttt{preprintlabel} command.}}


\maketitle

\section{Structure}
\begin{itemize}
    \item \verb|Preamble|
    \begin{itemize}
        \item \verb|packages.tex|: packages are imported here.
        \item \verb|commands.tex|: commands are defined here.
        \item \verb|settings.tex|: settings are defined here.
    \end{itemize}
\end{itemize}

\section{Settings}

The settings can be updated in the \verb|settings.tex| file.

\subsection{Margins}
Update \verb|\usepackage[margin=1in, top = 1in, bottom = 0.8in, headheight = 0.3in]{geometry}| as needed.

Update \verb|\setlength\parindent{0pt}| as needed.


\subsection{Anonymize paper for double blind reviews}
Replace \verb|\author{Steve}| with the following:
\begin{verbatim}
\author{
    \ifthenelse{\boolean{shownames}}%
    {Steve}%
    {Anonymous author(s)}%
}
\end{verbatim}

Use this block for other sensitive information. Change the \verb|\setboolean{shownames}{true}| setting to \verb|\setboolean{shownames}{false}|.

\subsection{Colors}

The commands in \secref{sec:commands} often use colors. These can be changed by modifying the following settings.
\begin{itemize}
    \item \verb|\newcommand{\newtextcolor}{blue}| -- sets the color of the added text annotations.
    \item \verb|\newcommand{\assignementcolor}{blue}| -- sets the color of the assignment annotations.
\end{itemize}





\section{Commands}\label{sec:commands}

\subsection{Frequently used annotations}

\begin{itemize}
    \item This is normal text.
    \item \TODO{This is a todo.}
    \item \TODO{} (Empty todo label.)
    \item \assignedto{Steve}
\end{itemize}

\hsep

\begin{itemize}
    \item Separating parts of texts might be useful occasionally. Use the \texttt{\textbackslash hsep} comment for the horizontal separator above.
\end{itemize}

\subsection{Review commands}

\begin{itemize}
    \item \rephrase{Should be rephrased}
    \item \id{This is my comment with my initials}
    \item \re{R1.01}{This marks a comment related to a reviewer's specific remark}
    \item \hl{This is a highlighting from the \texttt{soul} package for anything else.}
\end{itemize}

\subsection{Revision annotations}

\begin{itemize}
    \item \rem{Text removed.}
    \item \add{Text added.}
    \item \rep{Text replaced.}{New text.}
    \item \rem{Text with a reference{~\cite{bostrom2003are}} removed. -- Use braces around \texttt{$\sim$\textbackslash cite}.}
    \item \add{The \texttt{\textbackslash add\{\}} command does \textbf{NOT} support multiple paragraphs.}
    \item \addblockbegin{} Marking larger bodies of text as new is more efficient with placing it between a \texttt{\textbackslash addblockbegin\{\}} and \texttt{\textbackslash addblockend\{\}}. \addblockend{}
    
\end{itemize}

Some journals require submitting camera-ready revisions, but attaching the annotated version is advisable to enable traceability between the rebuttal and the revised manuscript, thus expiding things. Change the \verb|\setboolean{showannotations}{true}| setting to \verb|\setboolean{showannotations}{false}| to hide \verb|\add{}|, \verb|\rem{}| and \verb|\rep{}| annotations and produce the final version.


\subsection{Enumitem is loaded}

\begin{itemize}[noitemsep,topsep=0pt]
    \item Use \verb|\begin{itemize}[noitemsep,topsep=0pt]| for listst with a dense layout.
\end{itemize}

\subsection{Citing}

Natbib is loaded.
\begin{itemize}
    \item Use \verb|\citep{}| or \verb|\cite{}| for regular citations: \cite{bostrom2003are}.
    \item Use \verb|\citet{}| for author name citations: \citet{bostrom2003are}.
\end{itemize}

\bibliographystyle{IEEEtranN}
\bibliography{bib/references}

\end{document}
